Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-02 paper/ms.tex
update paper

% BEGIN NUMBERS
\newcommand{\numberpcs}{29\ }  % 2019/06/28 unanimous gold
\newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
\newcommand{\sVIInumberlcs}{91{,}736\ }  % 2019/06/20 not allnan
\newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  As part of the Cluster Difference Imaging Photometric Survey
  (CDIPS), we have been processing the TESS full-frame images and
  making light curves of stars that could be members of stellar
  associations, moving groups, or open clusters.
  %
  Our eventual hope is to discover giant transiting planets with known
  ages, and probe the exoplanet size and separation distributions for
  planets younger than 1 Gyr.
  %
  In this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties that agree with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the additional spectroscopic, photometric,
  and imaging observations that are needed to verify (i) that these
  candidates are planets and (ii) that the host stars are cluster members.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting reports are available at
  \stscilink.
\end{abstract}

@@

\begin{figure}[!t]
    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
    \caption{
        Significance thresholds empirically defined for the transiting planet 
        search described in \S~\ref{subsec:identifying_ctois}. Each point represents the 
        TLS periodogram peak signal detection efficiency from one light curve.
        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
    }
    \label{fig:tlsresults}
\end{figure}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{tlsresult_sector6.png}%{ctoi_quilt.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf 12 of the \numberpcs candidate transiting planets identified
    in this work.} 
    Models are fit as described in \S~\ref{subsec:ctois}.
    The full set of model parameters are in Table~XXX and on
    exofop-TESS.
	\label{fig:ctoi_quilt}
	}
\end{figure*}

@@

Finally, the determine the names of the objects -- and whether they
had already been identified as TOIs or cTOIs -- we cross-referenced
based on a combination of the TIC identifier, spatial position, and
the ephemeris of each object.

@@

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 3: Transit diagnostics.} The plots show the maximally-detrended
		light curve (top); the phase-folded light curve centered on the primary transit
		(middle left); the phase-folded light curve centered on the secondary eclipse
		(middle right); the odd-numbered transits (lower left); and the
		even-numbered transits (lower right).
		The stellar parameters ($T_{\rm eff}, R_\star$) are taken from Gaia-DR2 
		when available.
		The first eight lines of text are parameters determined 
		from the best-fitting TLS model.
		The one exception is the planet radius, which uses the stellar radius
		as noted above.
		The ``flux contamination'' (\texttt{TICCONT}) from neighboring stars
		is {\it never} taken into account, because transit depth dilution does
		not affect image subtraction analyses in the same manner as 
		aperture-photometry reductions.
		To estimate the transit to occulation
		depth ratio,
		the phase-folded light curve is also coarsely fit via maximum likelihood
		by a sum of two gaussians.
		``AstExc'' refers to the Gaia-DR2 astrometric excess, which can indicate
		hints of astrometric binarity in the system.
		``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a 
		zero-eccentricity central transit based on the Gaia-DR2 stellar radius,
		and a stellar mass interpolated from the \citet{pecaut_intrinsic_2013} table,
		under the assumption that the star is a dwarf.%\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
		\label{fig:pg3}
	}
\end{figure*}

>>>>

% BEGIN NUMBERS
\newcommand{\numberpcs}{29\ }  % 2019/06/28 unanimous gold
\newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
\newcommand{\sVIInumberlcs}{91{,}736\ }  % 2019/06/20 not allnan
\newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
\newcommand{\pctoflcswithage}{77} %  2019/07/02 from hist_logt.png

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  As part of the Cluster Difference Imaging Photometric Survey
  (CDIPS), we have been processing the TESS full-frame images and
  making light curves of stars that could be members of stellar
  associations, moving groups, or open clusters.
  %
  Our eventual hope is to discover giant transiting planets with known
  ages, and probe the exoplanet size and separation distributions for
  planets younger than 1 Gyr.
  %
  In this study, we made \numberlcs light curves of candidate young
  stars, across \numberclusters distinct clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties that agree with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the additional spectroscopic, photometric,
  and imaging observations that are needed to verify (i) whether these
  candidates are planets and (ii) whether the host stars are cluster members.
  %
  We also comment on the possible utility of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting reports are available at
  \stscilink.
\end{abstract}

@@

\begin{figure}[!t]
    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \caption{
        Significance thresholds empirically defined for the transiting planet 
        search described in \S~\ref{subsec:identifying_ctois}. Each point represents the 
        TLS periodogram peak signal detection efficiency from one light curve.
        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
    }
    \label{fig:tlsresults}
\end{figure}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf 6 of the \numberpcs candidate transiting planets identified
    in this studies.}
	Black points are detrended flux measurements, phased to the
	best-fit orbital period, indicated in the lower right of each panel.
	Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
	shown with blue lines.
	For display purpses, $\pm 4$ transit durations of the
	light curves are displayed.
	The vetting reports for these objects are available at XXX.	%FIXME
	The Gaia source identifiers are
	a): 5605128927705695232, 
	b): 3125263468681400320, 
	c): 5510676828723793920, 
	d): 3007171311355035136, 
	e): 5617126180115568256, 
	f): 3220266049321724416.   
	\label{fig:ctoi_quilt}
	}
\end{figure*}

@@

Finally, to determine the names of the objects -- and whether they
had already been identified as TOIs or cTOIs -- we cross-referenced
based on a combination of the TIC identifier, spatial position, and
the ephemeris of each object.

@@

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Page 3: Transit diagnostics.} The plots show the
    maximally-detrended light curve (top); the phase-folded light
    curve centered over $\pm3$ transit durations of the primary
    transit (middle left); the secondary eclipse (middle right); the
    odd-numbered transits (lower left); and the even-numbered transits
    (lower right).
    The stellar parameters ($T_{\rm eff}, R_\star$) are taken from
    Gaia-DR2 Apsis pipeline results when available
    \citep{andrae_apsis_2018}.
    The first eight lines of text are parameters determined from the
    best-fitting TLS model.
    The one exception is the planet radius, which uses the stellar
    radius as noted above.
    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
    stars is {\it never} taken into account, because transit depth
    dilution does not affect image subtraction analyses in the same
    manner as aperture-photometry reductions.
    To estimate the transit to occulation depth ratio, the
    phase-folded light curve is also coarsely fit via maximum
    likelihood by a sum of two gaussians.
    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
    indicate hints of astrometric binarity in the system.
    ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
    zero-eccentricity central transit based on the Gaia-DR2 stellar
    radius, and a stellar mass interpolated from the
    \citet{pecaut_intrinsic_2013} table, under the assumption that the
    star is a dwarf.
    %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
		\label{fig:pg3}
	}
\end{figure*}
